---
title: "Weight of Fish"
author: "Cienna Baker-Salgado"
date: "Fall 2024"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
require(leaps)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.

## Perch

Find the best two predictors for the Perch weight.

```{r}
Perchwtall=lm(Weight~.-Weight,data=Perch)
summary.lm(Perchwtall)
```


```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 2,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```


##Which is best?  

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[3,]
```

```{r}
best.model <- lm(Weight~Height+Width,data=Perch)
summary(best.model)
```

```{r}
anova(best.model,Perchwtall)
``` 

### Best Models

The best models for the Perch would be all of the above.

### Best Two regressor model

The best option that uses both variables are width and height


## Pike

Find the best two predictors for the Pike weight.

```{r}
Pikehwtall=lm(Weight~.-Weight,data=Pike)
summary.lm(Pikehwtall)
```


```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 2,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```



##Which is best?  

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[3,]
```

```{r}
best.model <- lm(Weight~Height+Width,data=Pike)
summary(best.model)
```


```{r}
anova(best.model,Pikehwtall)
``` 

### Best Models

The best model used would be all of the above.

### Best Two regressor model

The best model that uses two variables would be Length1 and Length3.


## Roach

```{r}
Roachwtall=lm(Weight~.-Weight,data=Roach)
summary.lm(Roachwtall)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 2,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```



##Which is best?

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[3,]
```

```{r}
best.model <- lm(Weight~Length3+Width,data=Roach)
summary(best.model)
```


```{r}
anova(best.model,Roachwtall)
```


### Best Models

The best models out of each is all of the above.

### Best Two regressor model

Out of everything the best model using two variables is Length1 and Width.

## Final Summary Statements    

For the Perch section, the best model is all variables, the best variables with two regressors would be height and Width.

For the Pike section, the best model is all variables, the best variables with two regressors would be Length1 and Length3.

For the Roach section, the best model is all variables, the best variables with two regressors would be Length3 and Width.